Manuscript

### 2018-10-26 manuscript.Rmd
CTRP allgenes wilcoxon test results

knitr::kable(ccle_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

CTRP:
```{r, eval=FALSE}
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.vars = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
```

@@

knitr::kable(gdsc_data_allgenes[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

>>>>

knitr::kable(ccle_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

CTRP:
```{r, eval=FALSE}
ctrp <- read.delim("./data_munging/data_drug_auc_ctrp_10_12_2018.csv", sep = "\t", header  = TRUE, row.names = 1, check.names = FALSE)
ctrp <- merge(drug_meta, ctrp, by = "CID")
ctrp_melt <- melt(ctrp, id.var  s = c("CID", "Drug"), measure.vars = colnames(ctrp)[3:ncol(ctrp)], variable.name = "accession_id", value.name = "AUC")
ctrp_grid <- expand.grid("accession_id" = unique(ctrp_melt$accession_id), "Hugo_Symbol" = as.character(unique(crispr_data$Hugo_Symbol)))
ctrp_data_allgenes <- WilcoxonByDrugAllGenes(ctrp_melt, ctrp_grid, "CTRP")
saveRDS(ctrp_data_allgenes, "./data_munging/rds/ctrp_data_18Q3_allgenes.rds", compress = "xz")
```

```{r}
ctrp_data_allgenes <- readRDS("./data_munging/rds/ctrp_data_18Q3_allgenes.rds")
ctrp_data_allgenes <- ctrp_data_allgenes[order(ctrp_data_allgenes$p),]

knitr::kable(ctrp_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

knitr::kable(gdsc_data_allgenes[1:1000, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for point mutations in genes targeted in CRISPR screen (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```
